This tutorial is just a startup guide about the Azure Sphere device, Azure Security Services and the IOT. To have a complete demo 
about the Azure Sphere, there are still a lot of work to be done and some questions need to be solved.

\subsection{Remain Questions}
\begin{enumerate}
    \item The device was claimed under Jianyuan Ma's ÅF account, in the ÅF directory, because there is a tenant named "AFTechnology". 
          Please reference to the \ref{sec:install}. We have figure out how to create the tenant under directory "af sphere" and claim 
          a new device.
    \item The temperature reading is not read by the Azure Sphere device but the Arduino, due to the GPIO pins on Azure Sphere can not 
          change the mode after they have been opened and occupied. Jianyuan Ma did not find the best solution to operate the AM2302 
          sensor by Azure Sphere. 
\end{enumerate}

\subsection{Remain Works}
\begin{enumerate}
    \item Create an IoT service for the sensor reading from Azure Sphere.
    \item Setup a message routing in the IoT hub to receive the messages from Azure Sphere. The message routing can be found under the 
          IoT hub created in the \ref{subsec:Step1}. You may need to scroll down a little bit. The tutorial on how to create the messages
          routing can be found in \href{https://docs.microsoft.com/en-us/azure/iot-hub/tutorial-routing}{Configure message routing with IoT Hub}, 
          you may need to create a Service Bus Queue also, which can be found in \href{https://docs.microsoft.com/en-us/azure/service-bus-messaging/service-bus-dotnet-get-started-with-queues}{Get started with Service Bus queues}
    \item Create a web application to display the sensor messages into a diagram.
    \item Further studies on Azure Sphere, such as the \href{https://docs.microsoft.com/en-us/azure-sphere/deployment/deployment-overview}{Over-the-Air Deployment} and 
          other resources in the Azure Portal.
    \item The \href{http://wiki.seeedstudio.com/Azure_Sphere_MT3620_Development_Kit/}{Azure Sphere MT3620 Development Kit} might be a 
          very helpful to understand the Azure Sphere device, IoT hub, OTA application and Security Services.
\end{enumerate}