\subsection{What is Azure Sphere}
Azure Sphere is a secured, high-level application platform with built-in communication and security features for internet-connected devices.

Azure Sphere introduces a new class of secured, connected, crossover MCU, which integrates real-time processing capabilities with a high-level 
operating system. Together with the application platform and enables product manufacturers to create secured, internet-connected device, so that
it can be updated, controlled, monitored, and maintained remotely. By embedding the MCU in a connected device, either alongside or in place of 
existing MCU(s), product manufacturers gain enhanced security, productivity, and opportunity. For example:
\begin{itemize}
    \item A secured application environment and authenticated connection can minimize the security risks from the spoofing, rogue software or denial of 
    service attacks.
    \item Software updates can be automatically deployed over the air to any connected device to provide new functionalities ,fix problems or counter 
    emerging methods of attacks, thus enhancing the productivity of support personnel.
    \item The cloud can diagnosing problems and designing new products over a secured connection, thus increasing the opportunity for product service, 
    positive customer interactions, and future development.
\end{itemize}

The Azure Sphere Security Service provides a safely and securely connect to the cloud and web. The service ensures that the device boots only with an authorized 
version of genuine, approved software. In addition, it provides a secured channel through which Microsoft can automatically download and install operating system 
updates to deployed devices in the field to mitigate security issues. Neither manufacturer nor end-user intervention is required, thus preventing a common security gap.

To read more about the Azure Sphere Security Service, please visit \href{https://docs.microsoft.com/en-us/azure-sphere/product-overview/azure-sphere-seven-properties}{Azure Sphere and the Seven Properties}

